Area maximisation in continuous time

### 2013-11-09 Notes/ContTime.tex
cleanup of memory curve notes

We can rewrite \eqref{eq:areaT} as
%
\begin{equation}\label{eq:areaEta}
\begin{aligned}
  \hat{A} &= 2\sum_{i,j} \enc_{ij} \eq_i (\eta^+_{i} - \eta^+_{j}) &
    &= -2\sum_{i,j} \enc_{ij} \eq_i \eta^+_{j} \\
    &= 2\sum_{i,j} \enc_{ij} \eq_i (\eta^-_{j} - \eta^-_{i}) &
    &= 2\sum_{i,j} \enc_{ij} \eq_i \eta^-_{j}.
\end{aligned}
\end{equation}
%
We can also express it in terms of the fundamental matrix \eqref{eq:funddef} as
%
\begin{equation}\label{eq:areaZ}
  \hat{A} = \sum_{i,j,k,l} \enc_{ij} \pib_{l} \fund_{li} (\fund_{jk}-\fund_{ik}) \w_k
    = \pib \fund q \fund \w.
\end{equation}
%

It is also helpful to define the following quantities:
%
\begin{equation}\label{eq:areacoeffs}
  \begin{aligned}
    c_k &= \diff{\ln\eq_k}{\alpha}
      = \sum_{ij} \eq_i \enc_{ij} \prn{\fptb_{ik}-\fptb_{jk}}
      = - \prn{\eq q \fptb}_k
      = \frac{(\eq q \fund)_k}{\eq_k}, \\
    a_i &= \sum_j \enc_{ij} \eq_i (\eta^+_{i} - \eta^+_{j}),\\
    \implies
    \hat{A} &= \sum_k c_k \eq_k \w_k
      = 2\sum_i a_i.
  \end{aligned}
\end{equation}
%
Note that the optimal choice of $\w$ is $\w_k = \sgn(c_k)$.

@@

The SNR at time $t$ was given in \eqref{eq:SNRcurve} as
%
\begin{equation*}
  \SNR(t) = \sqrt{N} (2f^+f^-) \eq \enc \, \e^{rt\frg}\w.
\end{equation*}
%
Let us try to maximise this at time $t$ only.
We will consider the independent parameters to be the off-diagonal elements of $\M^\pm$, with the diagonal elements determined via $\M^\pm_{ii} = \sum_{j\neq i} \M^\pm_{ij}$.
Consider the Lagrangian
%
\begin{equation}\label{eq:finlagrangian}
  \CL = \eq \enc\e^{rt\frg}\w + \sum_\pm \sum_{ij} \mu^\pm_{ij} \M^\pm_{ij}.
\end{equation}
%
Necessary conditions for an extremum are
%
\begin{equation*}
  \pdiff{\CL}{\M^\pm_{gh}} = 0,
  \qquad
    \mu^\pm_{gh} \geq 0,\quad
    \M^\pm_{gh} \geq 0,\quad
    \mu^\pm_{gh}\M^\pm_{gh} = 0.
\end{equation*}
%
We can use the results of \cite{Ortiz2001diffmatexp} to write down the shift of this Lagrangian under an infinitesimal perturbation
%
\begin{equation}\label{eq:finpert}
\begin{aligned}
  \delta\CL =&\, \eq \delta\frg \fund\, \enc \, \e^{rt\frg} \w
    + \eq \delta\enc \, \e^{rt\frg} \w %\\ &
   + r\int_{0}^{t}\!\!\dr\tau\, \eq \enc\, \e^{r\tau\frg} \delta\frg \e^{r(t-\tau)\frg} \w\\
   &+ \sum_\pm \sum_{ij} \mu^\pm_{ij} \delta\M^\pm_{ij}
\end{aligned}
\end{equation}
%
This can be rewritten using the eigenvector decomposition of $\frg$.
%
\begin{equation}\label{eq:eigendecomp}
  \frg = \sum_a -q_a \uv^a \vv^a,
  \quad
  \vv^a \uv^b = \delta_{ab},
  \quad
  \frg \uv^a = -q_a \uv^a,
  \quad
  \vv^a \frg = -q_a \vv^a.
\end{equation}
%
People often write $\vv$ as $\vv\trans$, presumably because they find the concept of row vectors too difficult to handle.
We're better than that.
We can choose $q_1=0$, $\uv^1=\onev$ and $\vv^1=\eq$.

Then, defining
%
\begin{equation}\label{eq:eigdiff}
  F_{ab} = \left\{
           \begin{aligned}
             &rt\,\e^{-q_art}, &\quad&\text{if } q_a=q_b,\\
             &\frac{\e^{-q_art}-\e^{-q_brt}}{q_b-q_a}, &&\text{otherwise,}
           \end{aligned}
           \right.
\end{equation}
%
we get
%
\begin{equation}\label{findiff}
\begin{aligned}
  \pdiff{\CL}{\M^\pm_{gh}} =&\,
    f^\pm \eq_g \prn{\brk{\fund \, \enc \, \e^{rt\frg} \w}_h - \brk{\fund \, \enc \, \e^{rt\frg} \w}_g} \\
    &\pm \eq_g \prn{\brk{\e^{rt\frg} \w}_h - \brk{\e^{rt\frg} \w}_g} \\
    &+ \sum_{ab} F_{ab} (\eq\enc\uv^a) \vv^a_g (\uv^b_h-\uv^b_g) (\vv^a\w) \\
    &+ \mu^\pm_{gh} - \mu^\pm_{gg}.
\end{aligned}
\end{equation}
%

@@

Consider the Laplace transform of the evolution operator:
%
\begin{equation}\label{eq:levol}
  \mathbf{G}(s) = \int_0^{\infty}\dr t\, \e^{(\MM-s) t}.
\end{equation}
%
For $\Re s>0$, we have 
%
\begin{equation}\label{eq:levolcalc}
  (s-\MM)\mathbf{G}(s) = \int_0^{\infty}\dr t\, (s-\MM)\e^{(\MM-s) t} = \brk{-\e^{(\MM-s) t}}_0^{\infty} = \I.
\end{equation}
%
As $(s-\MM)$ is invertible for $\Re s>0$, because all eigenvalues of $\MM$ are nonpositive, we have 
%
\begin{equation}\label{eq:levolres}
  \mathbf{G}(s) = (s-\MM)\inv.
\end{equation}
%
For $s=0$, we can avoid our problems by replacing $\mathbf{G}(s) \to \fund(s)$.

Now consider the Laplace transform of the SNR curve \eqref{eq:SNRcurve}
%
\begin{equation}\label{eq:lsnr}
\begin{aligned}
  A(s) &= \int_0^{\infty}\dr t \e^{-st}\SNR(t) \\
   &= \int_0^{\infty}\dr t\, \sqrt{N}(2f^+f^-) \eq \enc \e^{(r\frg-s)t} \w \\
   &= \frac{\sqrt{N}(2f^+f^-)}{r} \eq \enc \prn{s - r\frg}\inv \w.
\end{aligned}
\end{equation}
%
This expression is ill-behaved at $s=0$.
Thanks to \eqref{eq:alfund}, we can solve this by the replacement $\mathbf{G}(s) \to \fund(s)$, as $\enc\onev=0$.
%
\begin{equation}\label{eq:larea}
\begin{aligned}
  \hat{A}(s) = \frac{rA(s)}{\sqrt{N}(2f^+f^-)} &=  \eq \enc \fund(s) \w \\
    &= \sum_{ijk} \eq_i \enc_{ij} \prn{\fptb_{ik}(s)-\fptb_{jk}(s)} \eq_k \w_k \\
    &= 2\sum_{ij}  \eq_i \enc_{ij} (\eta^+_{i}(s) - \eta^+_{j}(s)).
\end{aligned}
\end{equation}
%
Note that $A(0)=A$, the area, and $\lim_{s\to\infty} \brc{sA(s)} = \SNR(0)$, the initial SNR.

@@

Hopefully we can prove an upper bound on the Laplace transform of the memory curve:
%
\begin{equation}\label{eq:lbound}
  A(s) \leq \sqrt{N}B(s) = \frac{\sqrt{N}}{C(s)}.
\end{equation}
%
We will assume that $C(s)$ is a concave function.
We already know that $C(0)=\frac{1}{M-1}$ and $C(s) \to s$ as $s\to\infty$.

In the eigenmode decomposition, this reads
%
\begin{equation}\label{eq:lboundeig}
  \sum_a \frac{\CI_a}{q_a+s} \leq B(s).
\end{equation}
%
Now let's maximise $\snr(t_0)$ with respect to $\brc{\CI_a,q_a}$.
Consider the Lagrangian
%
\begin{equation}\label{eq:envlagrange}
  \CL = \sum_a \CI_a \e^{-q_a t_0} +\intd[_0^\infty]{s} \mu(s)\brk{B(s)-\sum_a\frac{\CI_a}{q_a+s}}.
\end{equation}
%
Necessary conditions for a maximum are
%
\begin{alignat}{3}
  \pdiff{\CL}{\CI_a} &= \e^{-q_a t_0} - \intd{s} \frac{\mu(s)}{q_a+s} = 0, \label{eq:envI}\\
  \pdiff{\CL}{q_a} &= \CI_a\brk{-t_0\e^{-q_a t_0} + \intd{s} \frac{\mu(s)}{(q_a+s)^2}} = 0, \label{eq:envq}\\
  \mu(s)\fdf{\CL}{\mu(s)} &= \mu(s)\brk{B(s)-\sum_a\frac{\CI_a}{q_a+s}} = 0, \label{eq:envKT}\\
  \mu(s) &\geq 0, \label{eq:envKTm}\\
  \fdf{\CL}{\mu(s)} &= B(s)-\sum_a\frac{\CI_a}{q_a+s} \geq 0 \label{eq:envKTbnd}.
\end{alignat}
%
If we assume $\CI_a \neq0$ for some $a$, then \eqref{eq:envI} and \eqref{eq:envq} read
%
\begin{equation}\label{eq:envnumexp}
\begin{aligned}
  \e^{-q_a t_0} &= \intd{s} \frac{\mu(s)}{q_a+s}, \\
  t_0\e^{-q_a t_0} &= \intd{s} \frac{\mu(s)}{(q_a+s)^2}.
\end{aligned}
\end{equation}
%
The second of these is the derivative of the first with respect to $q$, therefore the two curves in the first must touch each other tangentially at $q_a$.
As both curves are decreasing convex functions, it seems unlikely that this could happen at multiple values of $q$.
We will assume that there is a single non-zero $\CI_a=\CI$, with the corresponding $q_a=q$, in the following.

For \eqref{eq:envI} to have a solution, $\mu(s)$ must be nonzero for at least one value of $s$.
Then, by \eqref{eq:envKT}, we must saturate \eqref{eq:envKTbnd} at those values of $s$.
If there were more than two such values, $\CI$ and $q$ would be overconstrained.
Assume there are two such values, $s=s_0$ and $s=s_1$.
%
\begin{equation}\label{eq:sattwice}
\begin{aligned}
  \CI &= B(s_0)(q+s_0) = B(s_1)(q+s_1) \qquad
  \implies q &= \frac{s_0 B(s_0) - s_1 B(s_1)}{B(s_1)-B(s_0)}.
\end{aligned}
\end{equation}
%
Now the bound \eqref{eq:envKTbnd} reads
%
\begin{equation}\label{eq:satwicebnd}
\begin{aligned}
  B(s) \geq \frac{B(s_0)(q+s_0)}{q+s} &= \frac{s_0-s_1}{(s-s_1)C(s_0)+(s_0-s)C(s_1)}, \\
  xC(s_0)+(1-x)C(s_1) &\geq C(xs_0+(1-x)s_1),
\end{aligned}
\end{equation}
%
where we substituted $s=xs_0+(1-x)s_1$.
As we assumed that $C(s)$ is concave, this is impossible.

Therefore the bound must be saturated exactly once and $\mu(s)=\mu_0\delta(s-s_0)$.
Now \eqref{eq:envI}, \eqref{eq:envq} and \eqref{eq:envKT} read
%
\begin{equation}\label{eq:satonce}
  \mu_0 = (q+s_0)\e^{-qt_0},
  \qquad
  (q+s_0)t_0 = 1,
  \qquad
  \CI = \frac{B(s_0)}{t_0}.
\end{equation}
%
This satisfies \eqref{eq:envKTm}.
Now \eqref{eq:envKTbnd} tells us
%
\begin{equation}\label{eq:satoncebnd}
\begin{aligned}
  B(s) &\geq \frac{B(s_0)}{(q+s)t_0}, 
  \qquad\text{or}\qquad
  1 + (s-s_0)t_0 &\geq \frac{C(s)}{C(s_0)}.
\end{aligned}
\end{equation}
%
As the two sides are equal at $s=s_0$, it is necessary that they touch tangentially for this bound to be true elsewhere.
The linearity of the LHS and concavity of the RHS ensure that this is sufficient for the bound to be satisfied for all $s$.
This condition is
%
\begin{equation}\label{eq:envs0t0}
  t_0 = \frac{C'(s_0)}{C(s_0)}.
\end{equation}
%

The resulting SNR curve and envelope are
%
\begin{equation}\label{eq:env}
  \snr(t) = \frac{\e^{(s_0-1/t_0)t}}{C'(s_0)},
  \qquad
  \snr(t_0) = \frac{\e^{s_0t_0-1}}{C'(s_0)},
\end{equation}
%
where $s_0$ is determined as a function of $t_0$ by \eqref{eq:envs0t0}.

>>>>

We can rewrite \eqref{eq:areaT} as
%
\begin{equation}\label{eq:areaEta}
\begin{aligned}
  \hat{A} &= 2\sum_{i,j} \eq_i \enc_{ij} (\eta^+_{i} - \eta^+_{j}) &
    &= -2\sum_{i,j} \eq_i \enc_{ij} \eta^+_{j} \\
    &= 2\sum_{i,j} \eq_i \enc_{ij} (\eta^-_{j} - \eta^-_{i}) &
    &= 2\sum_{i,j} \eq_i \enc_{ij} \eta^-_{j}.
\end{aligned}
\end{equation}
%
We can also express it in terms of the fundamental matrix \eqref{eq:funddef} as
%
\begin{equation}\label{eq:areaZ}
  \hat{A} = \sum_{i,j,k,l} \pib_{l} \fund_{li} \enc_{ij} (\fund_{jk}-\fund_{ik}) \w_k
    = \pib \fund \enc \fund \w.
\end{equation}
%

It is also helpful to define the following quantities:
%
\begin{equation}\label{eq:areacoeffs}
  \begin{aligned}
    c_k &= \diff{\ln\eq_k}{\alpha}
      = \sum_{ij} \eq_i \enc_{ij} \prn{\fptb_{ik}-\fptb_{jk}}
      = - \prn{\eq \enc \fptb}_k
      = \frac{(\eq \enc \fund)_k}{\eq_k}, \\
    a_i &= \sum_j \eq_i \enc_{ij} (\eta^+_{i} - \eta^+_{j}),\\
    \implies
    \hat{A} &= \sum_k c_k \eq_k \w_k
      = 2\sum_i a_i.
  \end{aligned}
\end{equation}
%
Note that the optimal choice of $\w$ is $\w_k = \sgn(c_k)$.

@@

The SNR at time $t$ was given in \eqref{eq:SNRcurve} as
%
\begin{equation*}
  \SNR(t) = \sqrt{N} (2f^+f^-) \eq \enc \, \e^{rt\frg}\w.
\end{equation*}
%
Let us try to maximise this at time $t$ only.
We will consider the independent parameters to be the off-diagonal elements of $\M^\pm$, with the diagonal elements determined via $\M^\pm_{ii} = \sum_{j\neq i} \M^\pm_{ij}$.
Consider the Lagrangian
%
\begin{equation}\label{eq:finlagrangian}
  \CL = \eq \enc\, \e^{rt\frg}\w + \sum_\pm \sum_{ij} \mu^\pm_{ij} \M^\pm_{ij}.
\end{equation}
%
Necessary conditions for an extremum are
%
\begin{equation*}
  \pdiff{\CL}{\M^\pm_{gh}} = 0,
  \qquad
    \mu^\pm_{gh} \geq 0,\quad
    \M^\pm_{gh} \geq 0,\quad
    \mu^\pm_{gh}\M^\pm_{gh} = 0.
\end{equation*}
%
We can use the results of \cite{Ortiz2001diffmatexp} to write down the shift of this Lagrangian under an infinitesimal perturbation
%
\begin{equation}\label{eq:finpert}
\begin{aligned}
  \delta\CL =&\, \eq \delta\frg \fund\, \enc \, \e^{rt\frg} \w
    + \eq \delta\enc \, \e^{rt\frg} \w %\\ &
   + r\int_{0}^{t}\!\!\dr\tau\, \eq \enc\, \e^{r\tau\frg} \delta\frg \e^{r(t-\tau)\frg} \w\\
   &+ \sum_\pm \sum_{ij} \mu^\pm_{ij} \delta\M^\pm_{ij}
\end{aligned}
\end{equation}
%
This can be rewritten using the eigenvector decomposition of $\frg$.
%
\begin{equation}\label{eq:eigendecomp}
  \frg = \sum_a -q_a \uv^a \vv^a,
  \quad
  \vv^a \uv^b = \delta_{ab},
  \quad
  \frg \uv^a = -q_a \uv^a,
  \quad
  \vv^a \frg = -q_a \vv^a.
\end{equation}
%
People often write $\vv$ as $\vv\trans$, presumably because they find the concept of row vectors too difficult to handle.
We're better than that.
We can choose $q_1=0$, $\uv^1=\onev$ and $\vv^1=\eq$.

Then, defining
%
\begin{equation}\label{eq:eigdiff}
  F_{ab} = \left\{
           \begin{aligned}
             &rt\,\e^{-q_art}, &\quad&\text{if } q_a=q_b,\\
             &\frac{\e^{-q_art}-\e^{-q_brt}}{q_b-q_a}, &&\text{otherwise,}
           \end{aligned}
           \right.
\end{equation}
%
we get
%
\begin{equation}\label{findiff}
\begin{aligned}
  \pdiff{\CL}{\M^\pm_{gh}} =&\,
    f^\pm \eq_g \prn{\brk{\fund \, \enc \, \e^{rt\frg} \w}_h - \brk{\fund \, \enc \, \e^{rt\frg} \w}_g} \\
    &\pm \eq_g \prn{\brk{\e^{rt\frg} \w}_h - \brk{\e^{rt\frg} \w}_g} \\
    &+ f^\pm \sum_{ab} F_{ab} (\eq\enc\uv^a) \vv^a_g (\uv^b_h-\uv^b_g) (\vv^a\w) \\
    &+ \mu^\pm_{gh} - \mu^\pm_{gg}.
\end{aligned}
\end{equation}
%

@@

Consider the Laplace transform of the evolution operator:
%
\begin{equation}\label{eq:levol}
  \mathbf{G}(s) = \intd[_0^{\infty}]{t} \e^{(\MM-s) t}.
\end{equation}
%
For $\Re s>0$, we have 
%
\begin{equation}\label{eq:levolcalc}
  (s-\MM)\mathbf{G}(s) = \intd[_0^{\infty}]{t} (s-\MM)\e^{(\MM-s) t} = \brk{-\e^{(\MM-s) t}}_0^{\infty} = \I.
\end{equation}
%
As $(s-\MM)$ is invertible for $\Re s>0$, because the real part of all eigenvalues of $\MM$ are nonpositive, we have
%
\begin{equation}\label{eq:levolres}
  \mathbf{G}(s) = (s-\MM)\inv.
\end{equation}
%
For $s=0$, we can avoid problems by replacing $\mathbf{G}(s) \to \fund(s)$.

Now consider the Laplace transform of the SNR curve \eqref{eq:SNRcurve}
%
\begin{equation}\label{eq:lsnr}
\begin{aligned}
  A(s) &= \intd[_0^{\infty}]{t} \e^{-st}\SNR(t) \\
   &= \intd[_0^{\infty}]{t} \sqrt{N}(2f^+f^-) \eq \enc \e^{(r\frg-s)t} \w \\
   &= \frac{\sqrt{N}(2f^+f^-)}{r} \eq \enc \prn{s - r\frg}\inv \w.
\end{aligned}
\end{equation}
%
This expression is ill-behaved at $s=0$.
Thanks to \eqref{eq:alfund}, we can solve this by the replacement $\mathbf{G}(s) \to \fund(s)$, as $\enc\onev=0$.
%
\begin{equation}\label{eq:larea}
\begin{aligned}
  \hat{A}(s) = \frac{rA(s)}{\sqrt{N}(2f^+f^-)} &=  \eq \enc \fund(s) \w \\
    &= \sum_{ijk} \eq_i \enc_{ij} \prn{\fptb_{ik}(s)-\fptb_{jk}(s)} \eq_k \w_k \\
    &= 2\sum_{ij}  \eq_i \enc_{ij} (\eta^+_{i}(s) - \eta^+_{j}(s)).
\end{aligned}
\end{equation}
%
Note that $A(0)=A$, the area, and $\lim_{s\to\infty} \brc{sA(s)} = \SNR(0)$, the initial SNR.

@@

Hopefully we can prove an upper bound on the Laplace transform of the memory curve:
%
\begin{equation}\label{eq:lbound}
  A(s) \leq \sqrt{N}B(s) = \frac{\sqrt{N}}{C(s)}.
\end{equation}
%
We will assume that $C(s)$ is a concave function.
We already know that $C(0)=\frac{r}{M-1}$ and $C(s) \to s$ as $s\to\infty$.

In the eigenmode decomposition \eqref{eq:eigendecomp}:
%
\begin{equation}\label{eq:eigenmode}
  \snr(t) = \sqrt{N}\sum_a \CI_a\, \e^{-q_a t},
  \qquad
  \CI_a = (2f^+f^-) (\eq \enc \uv^a) (\vv^a \w)
\end{equation}
%
the upper bound reads
%
\begin{equation}\label{eq:lboundeig}
  \sum_a \frac{\CI_a}{q_a+s} \leq B(s).
\end{equation}
%
Now let's maximise $\snr(t_0)$ with respect to $\brc{\CI_a,q_a}$.
Consider the Lagrangian
%
\begin{equation}\label{eq:envlagrange}
  \CL = \sum_a \CI_a\, \e^{-q_a t_0} +\intd[_0^\infty]{s} \mu(s)\brk{B(s)-\sum_a\frac{\CI_a}{q_a+s}}.
\end{equation}
%
Necessary conditions for a maximum are
%
\begin{alignat}{3}
  \pdiff{\CL}{\CI_a} &= \e^{-q_a t_0} - \intd{s} \frac{\mu(s)}{q_a+s} = 0, \label{eq:envI}\\
  \pdiff{\CL}{q_a} &= \CI_a\brk{-t_0\,\e^{-q_a t_0} + \intd{s} \frac{\mu(s)}{(q_a+s)^2}} = 0, \label{eq:envq}\\
  \mu(s)\fdf{\CL}{\mu(s)} &= \mu(s)\brk{B(s)-\sum_a\frac{\CI_a}{q_a+s}} = 0, \label{eq:envKT}\\
  \mu(s) &\geq 0, \label{eq:envKTm}\\
  \fdf{\CL}{\mu(s)} &= B(s)-\sum_a\frac{\CI_a}{q_a+s} \geq 0 \label{eq:envKTbnd}.
\end{alignat}
%
If we assume $\CI_a \neq0$ for some $a$, then \eqref{eq:envI} and \eqref{eq:envq} read
%
\begin{equation}\label{eq:envnumexp}
\begin{aligned}
  \e^{-q_a t_0} &= \intd{s} \frac{\mu(s)}{q_a+s}, \\
  t_0\,\e^{-q_a t_0} &= \intd{s} \frac{\mu(s)}{(q_a+s)^2}.
\end{aligned}
\end{equation}
%
The second of these is the derivative of the first with respect to $q$, therefore the two curves in the first must touch each other tangentially at $q_a$.
As both curves are decreasing convex functions, it seems unlikely that this could happen at multiple values of $q$.
We will assume that there is a single non-zero $\CI_a=\CI$, with the corresponding $q_a=q$, in the following.

For \eqref{eq:envI} to have a solution, $\mu(s)$ must be nonzero for at least one value of $s$.
Then, by \eqref{eq:envKT}, we must saturate \eqref{eq:envKTbnd} at those values of $s$.
If there were more than two such values, $\CI$ and $q$ would be overconstrained.
Assume there are two such values, $s=s_0$ and $s=s_1$.
%
\begin{equation}\label{eq:sattwice}
\begin{aligned}
  \CI = B(s_0)(q+s_0) = B(s_1)(q+s_1) 
  \qquad
  \implies q = \frac{s_0 B(s_0) - s_1 B(s_1)}{B(s_1)-B(s_0)}.
\end{aligned}
\end{equation}
%
Now the bound \eqref{eq:envKTbnd} reads
%
\begin{equation}\label{eq:satwicebnd}
\begin{aligned}
  B(s) \geq \frac{B(s_0)(q+s_0)}{q+s} &= \frac{s_0-s_1}{(s-s_1)C(s_0)+(s_0-s)C(s_1)}, \\
  xC(s_0)+(1-x)C(s_1) &\geq C(xs_0+(1-x)s_1),
\end{aligned}
\end{equation}
%
where we substituted $s=xs_0+(1-x)s_1$.
As we assumed that $C(s)$ is concave, this is impossible.

Therefore the bound must be saturated exactly once and $\mu(s)=\mu_0\,\delta(s-s_0)$.
Now \eqref{eq:envI}, \eqref{eq:envq} and \eqref{eq:envKT} read
%
\begin{equation}\label{eq:satonce}
  \mu_0 = (q+s_0)\,\e^{-qt_0},
  \qquad
  (q+s_0)t_0 = 1,
  \qquad
  \CI = \frac{B(s_0)}{t_0}.
\end{equation}
%
This satisfies \eqref{eq:envKTm}.
Now \eqref{eq:envKTbnd} tells us
%
\begin{equation}\label{eq:satoncebnd}
\begin{aligned}
  B(s) \geq \frac{B(s_0)}{(q+s)t_0}, 
  \qquad\text{or}\qquad
  1 + (s-s_0)t_0 \geq \frac{C(s)}{C(s_0)}.
\end{aligned}
\end{equation}
%
As the two sides are equal at $s=s_0$, it is necessary that they touch tangentially for this bound to be true elsewhere.
The linearity of the LHS and concavity of the RHS ensure that this is sufficient for the bound to be satisfied for all $s$.
This condition is
%
\begin{equation}\label{eq:envs0t0}
  t_0 = \frac{C'(s_0)}{C(s_0)}.
\end{equation}
%

The resulting SNR curve and envelope are
%
\begin{equation}\label{eq:env}
  \snr(t) = \frac{\sqrt{N}\,\e^{(s_0-1/t_0)t}}{C'(s_0)},
  \qquad
  \snr(t_0) = \frac{\sqrt{N}\,\e^{s_0t_0-1}}{C'(s_0)},
\end{equation}
%
where $s_0$ is a function of $t_0$ determined by \eqref{eq:envs0t0}.
